Model

### 2019-05-08 stats/model.Rmd
investigate model parameters

---
title: "Model"
author: "M. Bohn"
output: html_document
---

@@

  var globalLineParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 1}),
    slope: uniformDrift({a: -3, b: 3, width: 1})
  }

@@

  // conceptually it might not make sense to have two sigmas, but maybe it does
  // intercept sigma probably will be smaller than slope sigma
  var item_int_sigma = uniformDrift({a: 0, b: 5, width: 0.2})

@@

      query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 3,
  cores = 3,
  inference_opts = list(method = "incrementalMH", 
                        samples = 2000, 
                        burn = 1000,
                        verbose = T,
                        verboseLag = 500)
)

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds")
```

@@

```{r}
ggplot(item_params, aes(x = value))+#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~item, scales = 'free')+
  theme_few()
```

@@

ggplot(global_params, aes(x = value))#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()
```

```{r}
ggplot(global_sigma, aes(x = value))+#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()
```

@@

```{r}
# speak_opt_params <- speak_opt %>%
#   group_by(parameter)%>%
#   summarise(mode = estimate_mode(value),
#             uci = hdi_upper(value),
#             lci = hdi_lower(value))
# 
# inv_model_data <- sem_know_model %>%
#   filter(Parameter != "speaker_optimality") %>%
#   mutate(Parameter = factor(Parameter)) %>%
#   separate(value, into = c("intercept", "slope"), 
#            sep = ", ") %>%
#   mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
#          slope = as.numeric(str_remove(slope, "[)]"))) %>%
#   rename(item = Parameter)%>%
#   group_by(item)%>%
#   summarise(sem_int = estimate_mode(intercept),
#             sem_slope = estimate_mode(slope))%>%
#   group_by(item)%>%
#   expand(sem_int,sem_slope,age = me_model_data$age)%>%
#   mutate(so_int = speak_opt_params%>%filter(parameter == "intercept")%>%pull(mode),
#          so_slope = speak_opt_params%>%filter(parameter == "slope")%>%pull(mode))%>%
#   mutate(speaker_optimality = so_int + so_slope * age,
#          semantic_knowledge = plogis(sem_int + sem_slope * age))

@@

```{r predictions pragmatic model ex 3 adults}
# inv_model_pred<- webppl(
#   program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
#   data =list(data = inv_model_data),
#   data_var = "dataFromR"
# )
# 
# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
# 
# inv_predictions <- inv_model_pred %>%
#   separate(`0`, into = c("item", "age"), sep="/")%>%
#   mutate(age = as.numeric(age))%>%
#   rename( me_effect = `1`)%>%
#   left_join(aoa_ratings)%>%
#   ungroup()%>%
#   mutate(item = fct_reorder(factor(item), mean_aoa), 
#          age = age + min(me_data$age_num))
```

@@

ggplot(plot_model_pred, aes(x=age+2,y = mode, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Inverse Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

@@

data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")
data_plot
```

>>>>

---
title: "Model"
output: html_document
---

@@

  var globalLineParameters = {
    intercept: uniformDrift({a: -3, b: 3, width: 1}),
    slope: uniformDrift({a: 0, b: 3, width: 1})
  }

@@

  // conceptually it might not make sense to have two sigmas, but maybe it does
  // intercept sigma probably will be smaller than slope sigma
  // var item_int_sigma = uniformDrift({a: 0, b: 3, width: 0.2})

@@

      // query.add(["modelPrediction", cndtn, age], [age, Math.exp(modelPredictions.score(1))])

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 4,
  cores = 4,
  inference_opts = list(method = "incrementalMH", 
                        samples = 2000, 
                        burn = 1000,
                        verbose = T,
                        #lag = 1,
                        verboseLag = 1000)
)

saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds")

sem_know_model <- sem_know_model %>%
  filter(Chain != 3)

@@

```{r}
ggplot(item_params, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~item, scales = 'free')+
  theme_few()
```

@@

ggplot(global_params, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~token, scales = 'free')+
  theme_few()
```

```{r}
ggplot(global_sigma, aes(x = value, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()
```

@@

```{r}
# speak_opt_params <- speak_opt %>%
#   group_by(parameter)%>%
#   summarise(mode = estimate_mode(value),
#             uci = hdi_upper(value),
#             lci = hdi_lower(value))
#

inv_model_data <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, mode)%>%
  expand(item, int,slope,age = unique(me_model_data$age- min(me_model_data$age)))%>%
  mutate(so_int = global_params_summary%>%filter(token == "speaker_optimality", parameter == "int")%>%pull(mode),
         so_slope = global_params_summary%>%filter(token == "speaker_optimality", parameter == "slope")%>%pull(mode))%>%
  mutate(speaker_optimality = so_int + so_slope * age,
         semantic_knowledge = plogis(int + slope * age))

@@

```{r predictions pragmatic model ex 3 adults}
inv_model_pred<- webppl(
  program_code = paste(rsaUtils, rsaModel, invPred , sep='\n'),
  data =list(data = inv_model_data),
  data_var = "dataFromR"
)
# 
# #saveRDS(inv_model_pred, "../saves/inv_model_pred.rds")
# #inv_model_pred <- readRDS("../saves/inv_model_pred.rds")
# 
inv_predictions <- inv_model_pred %>%
  separate(`0`, into = c("item", "age"), sep="/")%>%
  mutate(age = as.numeric(age))%>%
  rename( me_effect = `1`)%>%
  left_join(aoa_ratings)%>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa),
         age = age + min(me_data$age_num))
```

@@

ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Inverse Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

@@

data_plot <- ggplot(data = p2, aes(x = age_num, y = correct, col = familiar, fill = familiar)) +
  geom_hline(yintercept = 0.5, lty=2)+
  geom_jitter(width = 0, height = 0.05, alpha = .6)+
  geom_smooth(method = "loess", se = F, alpha = .5, span = 2)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  #facet_grid(~familiar)+
  ggtitle("Data")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")+
  scale_fill_viridis_d(name = "familiar object")

data_plot
```
